\documentclass[11pt,twocolumn]{article}
\usepackage{authblk}
\usepackage{pslatex, graphicx, amssymb, amsmath}
\usepackage{tikz}
\usepackage[hidelinks]{hyperref}
%%%% Redefine abstract environment
\def\abstract{
\typeout{Abstract}
 {\bf Abstract} 
} \def\endabstract{\par}


\begin{document}
\title{Solving the Carcassonne board game using reinforcement learning agents}
\author[1]{Bartosz Strzelecki}
\author[1]{Bogna Lew}
\author[1]{Jakub Kuczys}
\author[1]{Jakub Wierzba}
\author[1]{Krzysztof Pisarski}
\author[2]{Piotr Mironowicz}
\affil[1]{Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology, 80-233 Gdańsk, Poland}
\affil[2]{Department of Algorithms and System Modelling, Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology, 80-233 Gdańsk, Poland}


\maketitle
\begin{abstract}

  \input{abstract}
  
\end{abstract}

\input{sections/introduction.tex}

\input{engine_architecture.tex}

\input{sections/agent_architecture.tex}

\input{sections/experiment.tex}

\input{sections/results.tex}

\begin{thebibliography}{00}
\bibitem{AlphaGoAlgorithm}
Silver, D., Schrittwieser, J., Simonyan, K. et al.\ Mastering the game of Go without human knowledge. Nature 550, 354–359 (2017). \url{https://doi.org/10.1038/nature24270}

\bibitem{AlphaGoZero}
Silver, D., Schrittwieser, J., Simonyan, K. et al. Mastering the game of Go without human knowledge. Nature 550, 354–359 (2017). \url{https://doi.org/10.1038/nature24270}

\bibitem{AlphaGoBlog}
Google DeepMind. AlphaGo. \url{https://deepmind.google/research/breakthroughs/alphago/} (accessed: 28.05.2024)

\bibitem{AlphaGoZeroBlog}
David Silver and Demis Hassabis. Alpha{G}o {Z}ero: {S}tarting from scratch. \url{https://deepmind.google/discover/blog/alphago-zero-starting-from-scratch/} (accessed: 28.05.2024)

\bibitem{MasterThesisCarcassonne}
C. Heyden, Implementing a computer player for Carcassonne, Master's thesis, Department of Knowledge Engineering, Maastricht University, 2009,
pages 13-14.
% https://project.dke.maastrichtuniversity.nl/games/files/msc/MasterThesisCarcassonne.pdf

\bibitem{gopy}
The go-python Authors, gopy project: \url{https://github.com/go-python/gopy}

\bibitem{LanguageBindings}
Wikipedia contributors, Language binding, Wikipedia, The Free Encyclopedia, 2024:
\url{https://en.wikipedia.org/wiki/Language\_binding}

\bibitem{CarcassoneRules}
K. Wrede, Carcassonne rules, Z-Man Games, 2016.
% https://images.zmangames.com/filer\_public/d5/20/d5208d61-8583-478b-a06d-b49fc9cd7aaa/zm7810\_carcassonne\_rules.pdf

\bibitem{GolangPipeline}
S. Ajmani, Go Concurrency Patterns: Pipelines and cancellation, The Go Blog, 2014: \url{https://go.dev/blog/pipelines}

\bibitem{AlphaZero}
Silver, David; Hubert, Thomas; Schrittwieser, Julian; Antonoglou, Ioannis; Lai, Matthew; Guez, Arthur; Lanctot, Marc; Sifre, Laurent; Kumaran, Dharshan; Graepel, Thore; Lillicrap, Timothy; Simonyan, Karen; Hassabis, Demis (December 5, 2017). "Mastering Chess and Shogi by Self-Play with a General Reinforcement Learning Algorithm". arXiv:1712.01815 [cs.AI].
\end{thebibliography}
\end{document}
